---
title: "Raw .csv to mims"
output: html_notebook
---

This [R Markdown](http://rmarkdown.rstudio.com) Notebook shows how to convert accelerometer output files containing raw gravity as comma separated values (.csv) to Monitor Independent Movement Summary Units (MIMS-Unit) as explained in the [MIMS-Unit readme](https://rdrr.io/cran/MIMSunit/f/README.md).

## Require the 'MIMSunit' package.

Install if necessary.

```{r}
# Kudos to Henry - https://stackoverflow.com/questions/9341635/check-for-installed-packages-before-running-install-packages
mimsPackageName <- "MIMSunit"
if(mimsPackageName %in% rownames(installed.packages()) == FALSE) {
  install.packages(mimsPackageName)
}
library(mimsPackageName, character.only=TRUE)
```

## Need help?
```{r}
help("MIMSunit")
```

## Set Actigraph filename

```{r}
rawFilename <- "/Volumes/Accel/t_1/raw/700023t00c1.raw"
```

Import [ref](https://rdrr.io/cran/MIMSunit/man/import_actigraph_csv.html)

```{r}
default_ops = options()
options(digits.secs=3)

# Check file format
readLines(rawFilename)[1:15]

# Load the file without timestamp column
ptm_start <- proc.time()
time_sec = system.time(df = import_actigraph_csv(rawFilename))
ptm_end <- proc.time()

# Check loaded file
head(df)

# Check more
summary(df)
# Restore default options
options(default_ops)
```

That took `r ptm_end - ptm_start` to finish.

```r
system.time(df_mim <- MIMSunit::mims_unit(df, dynamic_range=c( -6, 6), epoch='1 min'))
```

# Import directly from a file

https://rdrr.io/cran/MIMSunit/man/mims_unit.html

```
mims_unit_from_files(
  files,
  epoch = "5 sec",
  dynamic_range,
  output_mims_per_axis = FALSE,
  use_gui_progress = FALSE,
  file_type = "mhealth",
  ...
)
```

# Obtain the mims value on a per second peoch

```r
system.time(mims_sec<-mims_unit_from_files(rawFilename, epoch="1 sec", dynamic_range=c(-6,6), file_type="actigraph", output_mims_per_axis=TRUE, use_gui_progress=TRUE))
```

# Write to a .csv

Writing to a file.

```{r}
basename(rawFilename)
# [1] "a.ext"
dirname(rawFilename)
# [1] "C:/some_dir"

#tools::file_path_sans_ext("ABCD.csv")

tools::file_path_sans_ext(rawFilename)

mimsOutfile = paste(tools::file_path_sans_ext(rawFilename),'.mims', sep='')

write.csv(mims_sec,mimsOutfile, row.names = FALSE)
```

### If there is something you need

-   enter it as a comment or bullet


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
